Drake Plan

### 2019-12-26 R/drake_plan_conus.Rmd
use here for directories

```{r}
# CONUS Drake Plans  ------------------------------------------------------------
source(here("R/drake_funcs.R"))
conus_plan <- drake_plan(
  # 1.  Aeroent ---------------------------------------------------------------------

@@

  shap_long = target(get_SHAP_long(cv_results),
                  transform = map(cv_results,.id = FALSE)),
  plotSHAP1 = target(plot_SHAP(shap_long),
                 transform = map(shap_long,.id = FALSE)),
  plotSHAP2 = target(plot_SHAP_scatter(cv_results, shap_long),
                 transform = map(cv_results, shap_long,.id = FALSE)),
  report = rmarkdown::render(
    knitr_in("AOD_CONUS_Report.Rmd"),
    output_file = file_out("AOD_CONUS_Report.html"),
    output_format = rmarkdown::html_document(toc = TRUE))
)
nemia_config <- drake_config(conus_plan_cv, cache = ssd_cache) # show the dependency
# vis_drake_graph(nemia_config, from = names(nemia_config$layout))
vis_drake_graph(nemia_config)
```

>>>>

```{r}
# CONUS Drake Plans  ------------------------------------------------------------
source(here("R/drake_funcs.R"))
conus_plan <- drake_plan(
  # 1.  Aeronet ---------------------------------------------------------------------

@@

  shap_long = target(get_SHAP_long(cv_results),
                  transform = map(cv_results,.id = FALSE)),
  plotSHAP1 = target(plot_SHAP(shap_long),
                 transform = map(shap_long,.id = FALSE)),
  plotSHAP2 = target(plot_SHAP_scatter(cv_results, shap_long),
                 transform = map(cv_results, shap_long,.id = FALSE)),
  report = rmarkdown::render(
    knitr_in(here("../AOD_CONUS_Report.Rmd")),
    output_file = file_out(here("../AOD_CONUS_Report.html")),
    output_format = rmarkdown::html_document(toc = TRUE))
)
nemia_config <- drake_config(conus_plan_cv, cache = ssd_cache) # show the dependency
# vis_drake_graph(nemia_config, from = names(nemia_config$layout))
vis_drake_graph(nemia_config)
```

### 2019-12-26 R/drake_plan_nemia.Rmd
use here for directories

# Libraries
suppressPackageStartupMessages({
  library(sf)
  library(magrittr)
  library(drake)
  library(data.table)
  library(fst)
  library(future)
  library(here)
  library(nngeo)
  library(ggplot2)
  library(SHAPforxgboost)
})
# ** need to revise accordingly the path to your local Just_universal
source("~/liuyanguu/Just_universal/code/xgboost_cvtune.R")
source("~/liuyanguu/Just_universal/code/xgboost_cv_RFE.R")

>>>>

# Libraries
suppressPackageStartupMessages({
  library(sf)
  library(magrittr)
  library(drake)
  library(data.table)
  library(fst)
  library(future)
  library(here)
  library(nngeo)
  library(ggplot2)
  library(SHAPforxgboost)
})
# ** need to revise accordingly the path to your local Just_universal
source(here("../Just_universal/code/xgboost_cvtune.R"))
source(here("../Just_universal/code/xgboost_cv_RFE.R"))
